### 2016-07-03 paper/extended-example.tex
added authors

LastCommaFirstName = Name", " Name
		(" " (Name | Initial))*
BibTexAuthor = ("" | ("author={" LastCommaFirstName
		(" and " LastCommaFirstName)* "},"))

FullName = Name (" " (Name | Initial))*
	(" " Name)
EndNoteAuthor = ("%A " FullName "\n")*

BibEndAuthorConv : BibTexAuthor <=> EndNoteAuthor = ?
\end{lstlisting}

>>>>

BNames = Name", " Name (" " (Name))*
Bib = ("" | ("author={" BNames (" and " BNames)* "},"))

ENames = Name (" " (Name))* (" " Name)
End = ("%A " ENames "\n")*

BibEnd : Bib <=> End = ?
\end{lstlisting}
